%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {IT Specialist} % Job title
    {Bahlsen Polska} % Organization
    {Skawina, Poland} % Location
    {Nov. 2020 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {HRM systems management (Teta, XPrimer) - ensuring business continuity and development of HRM systems; updating systems and application servers.}
        \item {Close cooperation with business team on change and incident requests.}
        \item {Continuous improvement of the level of IT services.}
        \item {Liasing with third party software vendors to resolve external issues.}
        \item {Management of mobile devices (tablets, smartphones, production terminals); purchasing and configuration.}
        \item {Managing telecommunications services (cooperation with providers of mobile and VoIP services)}
        \item {Utilized strong interpersonal and communications skills to serve customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Operation Service Desk Specialist} % Job title
    {Vesuvius} % Organization
    {Krakow, Poland} % Location
    {Jul. 2019 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Global VIP support}
        \item {International field support (England, Belgium, France)}
        \item {Basic monitoring virtual servers performance}
        \item {Categorizing and prioritizing end user support requests by utilizing ticketing system to provide up-to-date status and escalate when needed}
        \item { Cooperation with Global IT Application teams on the 2nd and 3rd line}
        \item {Granting/Maintaining users accesses to internal network resources}
        \item {Performing On-call services / resolving critical business issues}
        \item {Environments and apps: Active Directory DS,Citrix Xenapp, Xen Desktops,Microsoft SCCM,VMware Horizon,Windows OS,Windows Server 2008-2019,VMware ESXi,Lotus Notes,Microsoft O365,Microsoft Azure,}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Services Specialist} % Job title
    {Qurate Retail Group Global Business Services} % Organization
    {Krakow, Poland} % Location
    {Jun. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided 24/7 Tier 1 help desk customer service, application and hardware support for international retail corporation}
        \item {Work in 3 different ticketing systems; Service Now, HPSM and Cherwell}
        \item {Troubleshooting of various software issues using virtual connection tools (VMware, SCCM)}
        \item {Active Directory and Exchange basic administration}
        \item {Microsoft Office and o365 software troubleshooting}
        \item {Active cooperation with almost 50 IT Teams as well as vendors}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {General Manager} % Job title
    {BarberLot} % Organization
    {Krakow, Poland} % Location
    {Mar. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing a team of 9 employees}
        \item {Administration by completing documents, accounting, placing a purchase order}
        \item {Time management}
        \item {Define employee functions and keep individual on task}
        \item {Representing the company at industry events}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administartor} % Job title
    {Jatomi Fitness} % Organization
    {Krakow, Poland} % Location
    {Apr. 2014 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database administration on the platform PerfectGym}
        \item {Team management[GM acting for 6 months]}
        \item{Placing purchase order}
        \item{Representing the company at industry events}
        \item{Difficult customer service}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
